Supplemental Information:\\ Harnessing Design Principles from Glass Sponges for Structurally Robust Lattice Structures

### 2018-09-12 Supplemental-FernandesWeaverBertoldi_AdvMaterials_2018.tex
.

\section{Designs Considered}
In this study, we focus on four different lattice configurations constrained to deform in an in-plane setting only. In an effort to provide a fair performance compassion between the different designs all of the respective lattice configurations, the total amount of material (i.e. volume or mass) is conserved. Moreover,  we consider a fixed volume ratio between non-diagonal and diagonal elements (chosen to match the sponge geometry) and two different shapes for the cross section of all lattice members: circular and rectangular.  For circular cross-sections  we stay consistent with the geometry found within the biological species. However, since slender members with circular cross section easily buckle out-of-plane when the structure is subjected to compression, to facilitate  fabrication and testing and to avoid out-of-plane buckling, we also consider a rectangular cross-section. \KB{how do you determine the aspect ratio of the rectangular cross section? I don't get the text that follows from here}

For this new cross-section type, we assume the structure to be sufficiently deep in plane in comparison the structural length scale (plane strain assumption) to avoid out of plane behavior. The cross-section is scaled accordingly with mass while maintaining the depth across all elements constant.

In order to allow for fabrication and testing of plane strain structures and to avoid out of plane buckling, we converted the biological observations of the cylindrical cross-section into a polygonal cross-section. For this new cross-section type, we assume the structure to be sufficiently deep in plane in comparison the structural length scale (plane strain assumption) to avoid out of plane behavior. The cross-section is scaled accordingly with mass while maintaining the depth across all elements constant.

To the determine the minimum cross-section depth a parametric simulation on the necessary depth was run for each structure. The overall minimum depth for all geometries was chosen an a factor of safety of 1.5 was chosen for the finial depth.

In the subsequent sections, we describe in detail the unit cells for the four different designs (Designs A-D).

%For this cross-section type we stay consistent with the geometry found within the biological species. Although, this geometry is difficult to realize and validate experimentally, the result for this geometry pose great value to the understanding of the biological species.

>>>>

\section{Designs Considered}
In this study, we focus on four different lattice configurations constrained to deform in an in-plane setting only. In an effort to provide a fair performance compassion between the different designs all of the respective lattice configurations, the total amount of material (i.e. volume or mass) is conserved. Moreover,  we consider a fixed volume ratio between non-diagonal and diagonal elements (chosen to match the sponge geometry) and two different shapes for the cross section of all lattice members: circular and rectangular.  For circular cross-sections  we stay consistent with the geometry found within the biological species. However, since slender members with circular cross section easily buckle out-of-plane when the structure is subjected to compression we must mitigate the issue by pursuing a plane-strain structure such that it's depth slenderness ratio is sufficiently deep to avoid out-of-plane buckling. In order to address this, we converted the biological observations of the cylindrical cross-section into a polygonal section. For this new cross-section type, we assume the structure to be sufficiently deep in plane in comparison the structural length scale (plane strain assumption) to avoid out of plane deformation. The out-of-plane slenderness is scaled accordingly with mass to maintain the depth across all elements constant. To the determine the minimum cross-section depth a parametric simulation on depth was run to determine the necessary depth for each structure. The overall minimum depth for all geometries was chosen an a factor of safety of 1.5 was chosen for the finial depth.

For this new cross-section type, we assume the structure to be sufficiently deep in plane in comparison the structural length scale (plane strain assumption) to avoid out of plane behavior. The cross-section is scaled accordingly with mass while maintaining the depth across all elements constant. In the subsequent sections, we describe in detail the unit cells for the four different designs (Designs A-D).
